Contextual Identity: Freedom to be all Your Selves

### 2013-03-07 paper.tex
ispell, last read through (probably)

\begin{abstract}
We examine \textit{contextual identity}, a notion that individuals reveal
different aspects of themselves depending on context. At any given time,
an individual may act as a friend, relative, spouse, co-worker, aquaintance, or
stranger. We analyze contextual identity from the perspective of user choice
and control, survey contextual identity violations, and propose new resesarch
directions to enable users to have better control over their contextual
identities.
\end{abstract}

@@

Lesbian, gay, bisexual, and transgendered youth are at risk for contextual
identity violations.  Access to support is crucial for LGTB-identified youth,
who are at higher risk for bullying and suicide~\cite{hrc}, and
much of that support is only accessible through the Internet in socially
conservative areas. In 2011 Bobbi Duncan and Taylor McCormick, two
students at the University of Texas at Austin, were inadvertantly outed when
their choir director added them to a Facebook group for Queer
Chorus~\cite{fowler}. Even though both students had blocked their parents from
seeing any personal posts revealing their sexuality, Queer Chorus is a
public group and so Facebook published notifications to Duncan's and McCormick's
friends, including their parents. Duncan later attempted suicide~\cite{duncan}.

@@

The following examples illustrate how individuals attempt to preserve boundaries
between identities. None of these techniques are failsafe, but they serve as
useful reminders that perfect solutions may not be necessary or even desirable,
especially in the case where information leaks by casual or accidental
inspection.

@@

\paragraph{Service settings} Service configurations such as Facebook friends,
Google circles and privacy settings are intended for users to self-manage
privacy and identity. However, shifting privacy settings and complex,
interacting features make these configurations unpredictable for many users.
According to Pew Internet, 71\% of users change privacy-related settings; yet
the large number of users who experience regret on social networks indicates
that these settings are not working as intended~\cite{pew3}.

\paragraph{Auditing} Wang et. al suggest that common techniques
for handling regret online include manual deletion of regret- table posts,
self-censoring or delaying posts that they predict might bring
regret~\cite{wang}. Pew Internet reports that 57\% of Internet users
periodically search for themselves to manage reputation, with young adults
being the most active~\cite{pew3}.

@@

Service providers compete for customers by providing a platform that
meets all of their needs.  The multiplicity of social media means that
in order to be competitive, social networks encourage cross-linking,
resharing, and resyndication --- all of which promote linking identities.
Linking identities is already easy;
users need more tools to help separate and curate identities. Without
knowing more about how people think about identity, we concentrate solely on
automating manual processes that users already perform.

@@

\paragraph{Auditing}
A browser is in an ideal position to intermediate social network
posts, aggregate them locally, and present them to its user when she wants to
audit her digital footprint.  For example, people could inspect all of the
comments and posts they made in the last week and redact content that is
sensitive or too negative, a frequent cause of regret~\cite{wang}. 
Such a tool could incorporate sentiment analysis to aid its user in finding
particularly problematic content.

@@

\begin{comment}
\section{Acknowledgements}
The authors thank
Lucas Adamski
Ben Adida
Mike Connor
Chris Karlof
\end{comment}

>>>>

\begin{abstract}
We examine \textit{contextual identity}, a notion that individuals reveal
different aspects of themselves depending on context. At any given time,
an individual may act as a friend, relative, spouse, co-worker, acquaintance, or
stranger. We analyze contextual identity from the perspective of user choice
and control, survey contextual identity violations, and propose new research
directions to enable users to have better control over their contextual
identities.
\end{abstract}

@@

Lesbian, gay, bisexual, and transgendered youth are at risk for contextual
identity violations.  Access to support is crucial for LGTB-identified youth,
who are at higher risk for bullying and suicide~\cite{hrc}, and
much of that support is only accessible through the Internet in socially
conservative areas. In 2011 Bobbi Duncan and Taylor McCormick, two
students at the University of Texas at Austin, were inadvertently outed when
their choir director added them to a Facebook group for Queer
Chorus~\cite{fowler}. Even though both students had blocked their parents from
seeing any personal posts revealing their sexuality, Queer Chorus is a
public group and so Facebook published notifications to Duncan's and McCormick's
friends, including their parents. Duncan later attempted suicide~\cite{duncan}.

@@

The following examples illustrate how individuals attempt to preserve boundaries
between identities. None of these techniques are fail-safe, but they serve as
useful reminders that perfect solutions may not be necessary or even desirable,
especially in the case where information leaks by casual or accidental
inspection.

@@

\paragraph{Service settings} Features such as Facebook friends,
Google circles and privacy settings presumably allow users to manage their
privacy and identity. However, shifting implementations and complex,
interacting features make these configurations unpredictable for many users.
According to Pew Internet, 71\% of users change privacy-related settings; yet
the large number of users who experience regret on social networks indicates
that these settings are not working as intended~\cite{pew3}.

\paragraph{Auditing} Wang et al.~suggest that common techniques
for handling regret online include manual deletion of regret- table posts,
self-censoring or delaying posts that they predict might bring
regret~\cite{wang}. Pew Internet reports that 57\% of Internet users
periodically search for themselves to manage reputation, with young adults
being the most active~\cite{pew3}.

@@

The multiplicity of social media means that
in order to be competitive, social networks encourage cross-linking,
resharing, and resyndication --- all of which promote linking identities.
Linking identities is already easy;
users need more tools to help separate and curate identities. Without
knowing more about how people think about identity, we concentrate solely on
automating manual processes that users already perform.

@@

\paragraph{Auditing}
A browser is in an ideal position to intermediate social network
posts, aggregate them locally, and present them to its user when she wants to
audit her digital footprint.  For example, people could inspect all of the
comments and posts they made in the last week and redact content that is
sensitive or too negative, a frequent cause of regret~\cite{wang}. 
Such a tool could incorporate sentiment analysis to find
particularly problematic content.

@@

\begin{comment}
\section{Acknowledgments}
The authors thank
Lucas Adamski
Ben Adida
Mike Connor
Chris Karlof
\end{comment}
